---
title: "Homework 1: ggplot2"
author: "Valentina Bozok"
date: "2019-03-06"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
```

By using *mpg* dataset:

####1. Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables?

*Answer: Continuous variables are colored gradiently and categorical variables define distinct color to each category independently. Analogically with the other aesthetics.*

- Color
```{r}
ggplot(data = mpg) +
  geom_jitter(mapping = aes(x = cyl, y = displ, color = hwy))
```

- Size
```{r}
ggplot(data = mpg) +
  geom_jitter(mapping = aes(x = cyl, y = displ, size = hwy))
```

- Shape

*A continuous variable can not be mapped to shape*



####2. What happens if you map the same variable to multiple aesthetics?

```{r}
ggplot(data = mpg) +
  geom_jitter(mapping = aes(x = cyl, y = displ, size = hwy, color = hwy))
```


####3. What does the stroke aesthetic do? What shapes does it work with? (Hint: use ?geom_point)

*Answer: Stroke defines the thicknes on the border of the shape, so it obviously works only for shapes with fill and outline.*


```{r}
ggplot(data = mpg) +
  geom_jitter(mapping = aes(x = cyl, y = displ),shape = 23, fill = 'red', stroke = 1)
```
```{r}
ggplot(data = mpg) +
  geom_jitter(mapping = aes(x = cyl, y = displ), shape = 23, fill = 'red', stroke = 3)
```



####4. What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)?

```{r}
ggplot(data = mpg) +
  geom_jitter(mapping = aes(x = cyl, y = displ, size = hwy, color = hwy < 25))
```
